Proposed Solution

### 2017-01-24 CAV17/secs/postanal.tex
clarify some stuff and restructure definitions

as measured by the learner for that relationship. For notational
convenience, later in this section
we shall define $w_{V_1, V_2, l}$ as the weight of the
hyperedge $(V_1, V_2, l, w)$, and $s_{v_1, v_2, l}$ as the sum of weights
over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
\markk{define s explicity as a sum, using E notation from complexity}
We will refer to this hypergraph as the {\bf Rule Graph}
in further analysis.

Note that due to support / confidence assertions in the learner, we
may be assured that all weights in the graph are positive.

@@

    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} s_{x, v, l} + \sum_{l \in L} \sum_{v \in V} s_{v, x, l}$$

@@

We define a measurement of complexity based on the calculated correlation.
For a configuration file with a set of keywords $K$ for a system
with a Rule Hypergraph $H = (V, E)$, we first define $E_{source}(V_s, V_t)$ as
the set of all hyperedges where a vertex $v_1 \in V_s$ is in the source set and
a vertex $v_2 \in V_t$ is in the target. Finally we define the size
of an edge set $|E|$ to be the sum over all weights in the edge set.

@@

\begin{equation}
    COMPLEXITY(K, H) = \sum_{k \in K} \
        \begin{cases}
            1 * (1 - \frac{|E(k, K)|}{|E(k, V)|}) & \text{if}\ \ |E(k, V)| > 0 \\
            1 & \text{otherwise}
        \end{cases}
\end{equation}

>>>>

as measured by the learner for that relationship. We will also denote
$E_{V_1, V_2}$ as
the set of all hyperedges where a vertex $v_1 \in V_s$ is in the 
source set and a vertex $v_2 \in V_t$ is in the target. Sometimes we
will write a single vertex $v$ in our subscript, as notational convenience
for the singleton set containing $v$.

The size of an edge set is the sum of all weights in that set, so:

    $$|E_{v_1, v_2}| = \sum_{(X, Y, l, w) \in E_{v_1, v_2}} w$$

We will refer to this hypergraph as the {\bf Rule Graph}
in further analysis.

We note that support and confidence assertions in the learner ensure
that all weights are positive.

@@

    $$DEGREE(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$

@@

We define a measurement of complexity based on the calculated correlation.
For a configuration file with a set of keywords $K$ for a system
with a Rule Hypergraph $H = (V, E)$.

@@

\begin{equation}
    COMPLEXITY(K, H) = \sum_{k \in K} \
        \begin{cases}
            1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|}) & \text{if}\ \ |E_{k, V}| > 0 \\
            1 & \text{otherwise}
        \end{cases}
\end{equation}

Since all weights are positive, $|E_{k, V}| > 0$ if there is at least one 
edge in $E_{k, V}$. Examining $\frac{|E_{k, K}|}{|E_{k, V}|}$, we may think of this
term as the ratio of {\it possible} constraints on a keyword $k$ by all keywords
in the configuration space ($V$) to the {\it actual} constraints imposed in the
examined configuration file ($K$).
